### 2012-10-02 MSteenhagen-CV.tex
Updated information.

%% hyperlinks
\usepackage[xetex, 
	colorlinks=false,
	plainpages=false,
  	pdfpagelabels,
  	bookmarksnumbered,
  	pdftitle={\mytitle},
  	pagebackref,
  	pdfauthor={\myauthor},
  	pdfkeywords={\mykeywords}
  	]{hyperref}

@@

\ind Dissertation research on the nature of human experience of pictorial representations.

@@

\bigskip
\bigskip

@@

\ind 2012. MPhil Stud. research student. Dissertation: \emph{The Collective Image}. \vspace{-0.1in}

@@

\newpage

@@

@@

\ind 2012. Prins Bernhard Cultuurfonds (€10.000). \emph{Not used.}

\ind 2012. Hendrik Müller Vaderlandsch Fonds (€5.000). \emph{Not used.}

@@

@@

% \marginhead{{\vskip 0.3em}Publications}
% \medskip
% \noindent\emph{Book \vspace{0.01in}}
% \ind  Kieran Healy. 2006. \emph{\href{http://www.lastbestgifts.com}{Last Best Gifts: Altruism and the Market for Human Blood and Organs}}. Chicago:~University of Chicago Press. \vspace{-0.075in}

>>>>

%% hyperlinks
\usepackage[xetex, 
	colorlinks=true,
	plainpages=false,
  	pdfpagelabels,
  	bookmarksnumbered,
  	pdftitle={\mytitle},
  	pagebackref,
  	pdfauthor={\myauthor},
  	pdfkeywords={\mykeywords}
  	]{hyperref}

@@

\ind Dissertation research on the nature of human experience of pictorial representations. Supervisor: Prof. Mark Eli Kalderon.

@@

@@

\ind 2012. MPhil Stud. research student. Dissertation: \href{http://discovery.ucl.ac.uk/1348204/}{\emph{The Collective Image}}. Supervisors: Prof. Mark Eli Kalderon; Prof. Christopher Peacocke. \vspace{-0.1in}

@@

% \newpage

@@

\marginhead{{\vskip 0.3em}Publications}
\medskip

\ind  Steenhagen, M. 2010. `Explaining the Ugly,' \emph{Esthetica,} November.

\ind  Steenhagen, M. 2009. `Verwarring over lelijkheid,' \emph{Cimedart,} 39:2.

\ind  Steenhagen, M. 2008. `De keerzijde van liefde,' \emph{Cimedart,} 38:3.

@@

\ind 2012. Prins Bernhard Cultuurfonds (€10.000). \emph{Not taken up.}

\ind 2012. Hendrik Müller Vaderlandsch Fonds (€5.000). \emph{Not taken up.}

@@

\ind 2008. Chair of the organisation for \emph{The Philosopher's Rally,} an international graduate conference in Philosophy, Utrecht.

\marginhead{{\vskip 0.9em}IT-Skills}
\medskip

\ind Microsoft Office Suite; Adobe Acrobat Professional; Adobe Photoshop and Indesign; BibDesk/Endnote and TeX-based typesetting; HTML/PHP; Open Journal Systems.

\marginhead{{\vskip 0.9em}Languages}
\medskip

\ind Dutch (native); English (fluent); German (good).

@@
